---
title: "CER method for Weighted Mixed Tests"
format: html
editor: visual
---

## Example 8.2.2

Let $H_1$ denote the null hypothesis of no difference between the 100 mg/day dose and standard of care with respect to the primary endpoint. Let $H_2$ denote the null hypothesis of no difference between the 50mg/day dose and standard of care with respect to the primary endpoint. Let $H_3$ and $H_4$ denote corresponding null hypotheses for the high and low doses, respectively, with respect to the secondary endpoint.

**Testing Strategy**

```{r}
library(usethis)
library(devtools)
load_all()

##########################################
# Initial Weights
WI <- c(1 / 2, 1 / 2, 0, 0)

# Initial Transition Matrix
G <- matrix(
  c(
    0, 0.5, 0.5, 0,
    0.5, 0, 0, 0.5,
    0, 1, 0, 0,
    1, 0, 0, 0
  ),
  nrow = 4, byrow = T
)
# Graph
cordinates <- list(c(-1, 1), c(1, 1), c(-1, -1), c(1, -1))
gmcpPlot(WI = WI, G = G, hGroup = c("P", "P", "S", "S"), cordinates = cordinates)
```

**Weights for all Intersection hypothesis**

```{r}
WH <- data.frame(gMCPLite::generateWeights(g = G, w = WI))
colnames(WH) <- c(paste("H", 1:length(WI), sep = ""), paste("Weight", 1:length(WI), sep = ""))
WH
```

Inputs for Stage-1 analysis

```{r}
alpha <- 0.025 # Design alpha
nLooks <- 2 # number of looks
info_frac <- c(0.5, 1) # Information fraction
nArms <- 3 # number of arms
nEPs <- 2 # number of endpoints
nHypothesis <- (nArms - 1) + nEPs # number of hypothesis

ctrSS <- c(108, 216) # 2 stage cumulative Samples in Control arm
ctrSS <- c(50, 100) # look-wise planned sample Size in control arm
allocRatio <- c(1, 1, 1) # Arm-Wise planned Allocation ratio
sigma <- c(1, 1, 1) # Arm-wise planned standard deviation
```

Planned Boundaries for Parametric Weighted Dunnett H12,H13

```{r}
###############################  Inputs  #########################################
alpha <- 0.025 # Design alpha
allocRatio <- c(1, 1, 1) # Arm-Wise planned Allocation ratio
wJ <- c(0.5, 0.5) # Weights for the intersection hypothesis
######################### End of inputs #########################################
```
